Replication of Brydevall et al. 2018

### 2023-02-24 219-2023-analysis/manuscript.qmd
use osf to get data

@@

data.behavioral <- read_csv("data/preprocessed/behavioral.csv")

@@

We pre-registered an inclusion criteria that a participant must have at least 20 usable epochs of data of a particular event type in order to be included in the corresponding analyses. The minimum number of usable epochs for the RPE analysis in an individual subject was `r rpe.segments %>% pull(n) %>% min()`, *M*=`r rpe.segments %>% pull(n) %>% mean() %>% round(0)`, *SD*=`r rpe.segments %>% pull(n) %>% sd() %>% round(0)`. The minimum number of usable epochs for the IPE analysis in an individual subject was `r ipe.segments %>% pull(n) %>% min()`, *M*=`r ipe.segments %>% pull(n) %>% mean() %>% round(0)`, *SD*=`r ipe.segments %>% pull(n) %>% sd() %>% round(0)`. Therefore, no participants needed to be excluded from the following analyses.

@@

rpe.erp.data.subject <- data.eeg.filtered.rpe.ipe %>%
  filter(rpe_type != "None") %>%
  group_by(subject, electrode, t, rpe_type) %>%
  summarize(m.subject = mean(v))

@@

ipe.erp.data.subject <- data.eeg.filtered.rpe.ipe %>%
  filter(ipe_type != "None") %>%
  group_by(subject, electrode, t, ipe_type) %>%
  summarize(m.subject = mean(v))

>>>>

## Methods

data.behavioral <- read_csv("data/preprocessed/behavioral.csv")
```

### Participants

```{r}
#| label: Count participants
#| echo: false

n.participants <- data.behavioral %>% pull(subject_id) %>% unique() %>% length()
```

`r n.participants` Vassar College students participated in this study. All participants were right-handed.

@@

@@

```{r}
#| label: Exclude bad EEG
#| echo: false

bad.eeg.subjects <- rpe.segments %>% 
  filter(n < 20) %>% 
  bind_rows(ipe.segments %>% filter(n < 20)) %>%
  pull(subject) %>%
  unique()
```

We pre-registered an inclusion criteria that a participant must have at least 20 usable epochs of data of a particular event type in order to be included in the corresponding analyses. The minimum number of usable epochs for the RPE analysis in an individual subject was `r rpe.segments %>% pull(n) %>% min()`, *M*=`r rpe.segments %>% pull(n) %>% mean() %>% round(0)`, *SD*=`r rpe.segments %>% pull(n) %>% sd() %>% round(0)`. The minimum number of usable epochs for the IPE analysis in an individual subject was `r ipe.segments %>% pull(n) %>% min()`, *M*=`r ipe.segments %>% pull(n) %>% mean() %>% round(0)`, *SD*=`r ipe.segments %>% pull(n) %>% sd() %>% round(0)`. `r bad.eeg.subjects %>% length()` subject was excluded for poor EEG data quality.

@@

rpe.erp.data.subject <- data.eeg.filtered.rpe.ipe %>%
  filter(rpe_type != "None") %>%
  filter(!subject %in% bad.eeg.subjects) %>%
  group_by(subject, electrode, t, rpe_type) %>%
  summarize(m.subject = mean(v))

@@

ipe.erp.data.subject <- data.eeg.filtered.rpe.ipe %>%
  filter(ipe_type != "None") %>%
  filter(!subject %in% bad.eeg.subjects) %>%
  group_by(subject, electrode, t, ipe_type) %>%
  summarize(m.subject = mean(v))
